Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-07-05 ijar-npb-ms.tex
getting figures B.9, B.10 and B.11 on one page again

Clearly the true functioning probability, $p$, is unknown.  Figure \ref{fig:need-to-opt-45} therefore shows the worst case scenario for choice of $y$ --- that is, where the maximum of each curve from the previous subsection is taken.

>>>>

Clearly the true functioning probability, $p$, is unknown.  Figure \ref{fig:need-to-opt-45} therefore shows the worst case scenario for any choice of $y$ --- that is, where the maximum of each curve from the previous subsection is taken.
